### 2023-09-27 accepted/COPSolver/manuscript.tex
updating files

\noindent
\textbf{Abstract}\\
COPSolver is an open source software originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has a application of Fraga's exact method for solving the multi-product p-batch processing time maximization problem. Such application can have significant impacts on software development for efficiently solving p-batch problems as well as contributing to better inventory control in some industries. Also it can be applied to conduct case studies, contributing to teaching and research. This paper address the first version of COPSolver as well as some important aspects of this software and the next steps that will be implemented for it's applications development.
\vskip0.5cm

>>>>

\noindent
\textbf{Abstract}\\
COPSolver is an open source software originally developed to solve decision and/or optimization problems, especially from the combinatory optimization area. The first version of COPSolver has a application of Fraga's exact method for solving the multi-product p-batch processing time maximization problem. Such application can have significant impacts on software development for efficiently solving p-batch problems as well as contributing to better inventory control in some industries. Also it can be applied to conduct case studies, contributing to teaching and research. This paper address some important aspects of COPSolver and the next steps that will be implemented for it's applications development.
\vskip0.5cm
